Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} Model System

### 2014-05-31 trunk/paper_enahpc14/Sec3:Environment-setup.tex
Submitted version

\item \tinto is  a heterogeneous cluster composed of  28 compute nodes
  at UJI.  For our experiments only  a subset of  16 homogeneous nodes
  was  considered. Each  node  is  comprised of  two  Intel Xeon Westmere EP E5645
  hexa-core processors  running at  2.4\,GHz, equipped with  24\,GB of
  DDR3  1333\,MHz and  connected via  InfiniBand QDR  with  a Mellanox
  MTS\-3600 switch. Power saving mechanisms enabled on the nodes are the C-states C1, C3 and C6, 
  but no P-states (except P0) are used. TurboBoost feature is enabled for our experiments.
\end{itemize}

>>>>

\item \tinto is  a heterogeneous cluster composed of  28 compute nodes
  at UJI.  For our experiments only  a subset of  16 homogeneous nodes
  was  considered. Each  node  is  comprised of  two  Intel Xeon Westmere EP E5645
  hexa-core processors  running at  2.4\,GHz, equipped with  24\,GB of
  DDR3  1333\,MHz and  connected via  InfiniBand QDR  with  a Mellanox
  MTS\-3600 switch. 
\end{itemize}

Power saving mechanisms enabled on all the nodes' platforms were the C-states (C1, C3 and C6) 
and P-states, but only P0 or the maximum frequency was used. TurboBoost feature was also enabled for our experiments.
